A Simple and Strong Baseline for Universal Targeted Attacks on Siamese Visual Tracking

### 2021-05-06 博士/论文提交/adversarial_attack/TCSVT/latex/imperceptible.tex
补结论

>>>>

By studying the attack method of Siamese trackers, we argue that the disadvantage of Siamese trackers is that template matching-based tracking mechanism is vulnerable to attacks, i.e., if both the template and the search image are perturbed at the same time, then the tracking algorithm can easily be misled.
The implication for improving the tracking robustness is to make the tracker aware of the semantic information of the target being tracked, rather than relying on templates alone, so that the semantic information can be relied on to ensure tracking robustness.
